|

### 2021-04-09 appendix/appendix.Rmd
some edits to the appendix, more coming

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  if(class(mod)[1] == "rma.mv") {
    mod2 <- broom_mod(mod)
  } else {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  }

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {

  mod2 <- estim_het(dat = dat, 
                    yi = coef, 
                    v = v, 
                    random = ~ 1 | id_level1/id_level2, 
                    slab = slab, 
                    hetvar = hetvar)

  mod2 <- data.frame(mod2)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

@@

# Law of 1/n Model

In this section, we present the law of 1/n as formulated by @weingast1981political, and the refinement proposed by @primo2008distributive.

In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark. Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout all constituencies. The corollary of their model is that larger legislatures generate more public spending.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume that we will always employ a symmetric Nash equilibrium.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hire a local company to build the project). The second cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hire a company from another state). The third cost $c_3(x)$ captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

Following their model, the economic efficiency is achieved when the marginal costs are equal the marginal benefits of increase the project size. This leads to the economic optimal project size, $x^E$. The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$. However, the actual projects that are implemented have a different structure. First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represent the number of constituencies. Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms. Therefore, the benefits and costs of implement a project with size $x$ have the following structure:

@@

Totally differentiating $x$ with respect to $n$, gives us:

@@

Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size. The law of 1/n holds when the denominator is negative. $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$. Then, the law of 1/n is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

As the above condition suggests, the law of 1/n holds only in specific situations. @primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i. e., larger legislatures leading to lower expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i. e. how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Collecting terms, the citizens receive the following net benefit of a project with size $x$:

@@

Maximizing this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects yield to the following optimal project size:

@@

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive. Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX. Most of the literature after @weingast1981political, focused on complement their original formulation.

@@

XXXX CATARINA AND HUZEYFE: FIX THIS

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "*The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics*", which is a seminal contribution to the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in section \ref{sub:scrap} below. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles. XXXX CATARINA AND HUZEYFE: FIX THIS

@@

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were clearly unrelated to our topic of interest. For instance, we curiously found articles about car motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Then, we read all abstracts. We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were also included. This allowed us to significantly reduce our sample to 376 records.

In the second phase, we assessed full texts. To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure. If the publication had all three, it was maintained. Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.

@@

We selected the final pool of articles based on two criteria regarding their reported coefficients:

1.  Matched treatment variable:

@@

2.  Matched outcome variable:

@@

Our data are comprised of two datasets. The first dataset has the main coefficients reported in the studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.

@@

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Independent Variables") +
  coord_flip() +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal. The table below presents descriptive statistics for these moderators in our selection of articles.

```{r, warning=F, message=F, echo = FALSE, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T), caption = "Descriptive Statistics of Moderators")
```

@@

-   $H_0$: the proportion of positive and negative signs are indistinguishable ($p=0.5$).

As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) could be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

This test has two advantages. First, it is robust to the design of the paper. This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not. All these factors increase the levels of study heterogeneity. The binomial test ignores the design discrepancies and focuses on the overall reported effect. Second, this test has the advantage of being straightforward and easy to interpret. It requires very few assumption and has a direct statistical formulation. The disadvantage is that we can extract more information from the articles with meta-regressions, as we see in the next sections.

@@

Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

For the log of the number of legislators in the lower house ($\log(N)$), the results follow below.

@@

Out of `r sum(table(aux$scoef))`, `r as.numeric(table(aux$scoef)[2])` had a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

@@

Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` had a positive sign. The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$. This is the only test that presents evidence of an association between the legislature size and expenditure.

@@

In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models. The fixed effects model assumes that there exists only one true effect, and that all estimates are an attempt to uncover this effect. The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.

In this paper, we a random-effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

These sources of heterogeneity have two implications. First, they make our estimates notably disperse. All but one of our heterogeneity tests are significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:

@@

@@

The *law of 1/n* was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

@@

Now, we look into the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

@@

# Session Information

>>>>

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  if(class(mod)[1] == "rma.mv") {
    mod2 <- broom_mod(mod)
  } else {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()
  }
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod2 <- estim_het(dat = dat, 
                    yi = coef, 
                    v = v, 
                    random = ~ 1 | id_level1/id_level2, 
                    slab = slab, 
                    hetvar = hetvar)
  mod2 <- data.frame(mod2)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))
  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

@@

# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_

In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.

In their seminal paper, @weingast1981political argue that a high number of legislators will increase public spending beyond the optimal economic benchmark. They suggest that politicians have an incentive to over-provide concentrated benefits to their constituencies, spreading the costs across all constituencies through generalised taxation. The corollary of their model is that larger legislatures generate more public spending.

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hire a local company to build the project). The second cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hire a company from another state). The third cost $c_3(x)$, captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

Following their model, projects are economically efficient when the marginal costs are equal the marginal benefits of increase the project size. This leads to the economic optimal project size, $x^E$. The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$. However, the projects that are actually implemented have a different structure. First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies. Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms. Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:

@@

Totally differentiating $x$ with respect to $n$ gives us the following:

@@

Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size. The _law of 1/n_ holds when the denominator is negative. $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$. Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.

As the above condition suggests, the _law of 1/n_ holds only in specific situations. @primo2008distributive advances the theory by considering other situations where the law may not hold, and also argues that there are cases in which a reverse _law of 1/n_ holds, i. e., larger legislatures leading to lower expenditures.

Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country. Consider a local public good that generates a per capita benefit according to size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i. e. how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion). In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's. The degree that taxes are shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes $\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$. Collecting terms, the citizens receive the following net benefit of a project with size $x$:

@@

Maximising this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects, we find the following optimal project size:

@@

Therefore, we see that both the _law of 1/n_ and its reverse formulation are equally plausible. Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen_malhotra_2007], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].

@@

The first step in our systematic review consisted in gathering a study sample. We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature. This search produced a database with many entries that were unrelated to our subject of investigation. To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field. Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.

We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated. Our code is available in section \ref{sub:scrap} below. We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses. We set no restriction to unpublished articles.

We complemented this by doing a term search on Google Scholar after having finished the entire eligibility procedure on the first sample. We formulated the search string based on the terms and expressions that appeared most commonly in the articles included in our meta-analysis. The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending. The search string was as follows: *(“upper chamber size” OR "lower chamber size" OR “council size” OR “parliament size” OR “legislature size” OR “number of legislators” OR “legislative size") AND (“spending” OR “expenditure" OR “government size”)*. We scraped Google Scholar on March 5th, 2021. Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously. We then performed the exact same eligibility procedures, further explained below. This resulted in 3,041 additional records.

Combining the two search strategies, we assessed a total of 5,705 records.

@@

The selection process was conducted by two authors in three phases. In the first phase, we excluded all titles that were clearly unrelated to our topic of interest. This was only a preliminary step, as we were not able to eliminate a large number of entries. Then, we read all abstracts. We kept all publications whose main topics were either government expenditure or legislative structures. Abstracts that indicated that the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were included. This allowed us to significantly reduce our sample.

In the second phase, we assessed full texts. To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure. If the publication had all three, we kept it in our sample. Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. In this phase, we also collected information on whether the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.

@@

We selected the final pool of articles based on two criteria, namely the treatment and the outcome variables employed in the paper. The categories follow below:

1.  Treatment variables:

@@

2.  Outcome variables:

@@

Our meta-analytic data are comprised of two datasets. The first dataset has the main coefficients reported in the studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.

@@

```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=6, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Independent Variables") +
  coord_flip() +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal. The descriptive statistics for the moderators are available below.

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```

@@

-   $H_0$: the proportion of positive and negative signs are statistically equal ($p=0.5$).

As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true. In this case, the alternative hypothesis is $p\neq 0.5$. To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.

This test has two advantages. First, it is robust to the design of the paper. This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not. The binomial test ignores the design discrepancies and focuses on the overall reported effect. Second, this test has the advantages of requiring few assumptions and being easy to interpret. The disadvantage is that the test is not as informative as the meta-regressions, as we shall see in the next sections.

@@

Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

For the log of the number of legislators in the lower house ($\log(N)$), the results are as follows:

@@

Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])` have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

@@

Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$. This is the only test that presents evidence of an association between the legislature size and expenditure.

@@

In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models. The fixed effects model assumes that there exists a single true effect and all estimates are an attempt to uncover this effect. The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.

In this paper, we employ a random-effects model. The empirical papers testing the *law of 1/n* are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

@@

These sources of heterogeneity have two implications. First, they make our estimates notably disperse. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased. Thus, we opt for random effects model.

Assume that each study has an effect of $T_i$. In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:

@@

And to assess the possibility of publication bias, we add the funnel plot below:

@@

The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary indicator for electoral system.

@@

Now we look into the upper house size (*k*). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

@@
